Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-10-22 writeups/dissertation/dissertation.tex
foo

I would also like to mention a few open-sourced software packages that were heavily leveraged to do this research:
The majority of the modeling and analysis was done with the R statistical computing environment \parencite{RCoreTeam2014} and two important R packages:
data.table \parencite{Dowle2014} was leveraged to implement the models efficiently, and ggplot2 \parencite{Wickham2009} was used to produce the visualizations.

>>>>

I would also like to the creators of a few open-sourced software packages that were heavily leveraged to do this research:
The majority of the modeling and analysis was done with the R statistical computing environment \parencite{RCoreTeam2014} and two important R packages:
data.table \parencite{Dowle2014} was leveraged to implement the models efficiently, and ggplot2 \parencite{Wickham2009} was used to produce the visualizations.
